---
title: "hw0"
author: "Nigel Harriman"
format: html
---


# Defining our Function and Variables

I will be solving the below equation for x given any values of a, b, or c.

$$ f(x) = ax^2+bx+c = 0 $$
First, we will define our a, b, and c terms.

```{r}
#| echo: false
#Setting our values of a, b, and c
a <- 1
b <- 3
c <- 2
discriminant <- b^2 - 4*a*c

print(paste("The value of a is", a) ) 
print(paste("The value of b is", b) ) 
print(paste("The value of c is", c) ) 
```

Next, we solve for the roots. There can be 0, 1, or 2 solutions to the equation based on the values of a, b, and c.

```{r}
#| echo: false
#Setting up a function to solve the quadratic#
solve_quadratic <- function(a, b, c) {
  discriminant <- b^2 - 4*a*c
  #Two solutions#
  if (discriminant > 0) {
    root1 <- (-b + sqrt(discriminant)) / (2*a)
    root2 <- (-b - sqrt(discriminant)) / (2*a)
    print(paste("The roots of this equation are", root1, "and", root2) )
  #One solution#  
  } else if (discriminant == 0) {
    root <- -b / (2*a)
    print(paste("The root of this equation is", root) ) 
  } else {
  #No solutions#
    realPart <- -b / (2*a)
    imagPart <- sqrt(-discriminant) / (2*a)
    print(paste("There are no roots of this equation for those values of a, b, and c") )
  }
}
solve_quadratic(a, b, c)

```

# Graphing the Equation

Finally, we graph the equation using our specified values of a, b, and c within the x values of -5 to 5.
```{r}
#| echo: false
print(paste("Reminder: the value of a is", a) ) 
print(paste("Reminder: the value of b is", b) ) 
print(paste("Reminder: the value of c is", c) ) 
```

```{r}
#| echo: false
x <- seq(-5, 5, length = 300)
plot(x, a*x^2+b*x+c, type = "l")
abline(h = 0, lty = 2)

```
The values of our roots will be where the function intersects with the x-axis. If you do not see the function intersect with the x-axis, then there are no roots!
